Grove: A Convergent Collaborative Structure-Editor Calculus

### 2020-07-27 grove-paper.tex
Updates from Overleaf

@@

\subsubsection{Direct conflicts}

@@

We merge these by including \emph{both} edges as edges going out of the \texttt{body} index
of node~3.
This results in the bottom graph of Figure~\ref{fig:Direct Conflicts}.
The conflict between Alice's and Bob's changes is
represented by the fact that there are multiple edges going out of one index (i.e. the \texttt{body}
index of node~3).
In the graph representation, we flag this conflict by highlighting its edges
in red.
In the textual representation, we flag this conflict with the notation \texttt{\{ 2 | f x \}}.
This is a conflict that much eventually be resolved by the user by deleting
one of the edges and editing the other to be the merged value.
For example, one could delete edge~10 and then edit the \texttt{x}
to be \texttt{x + 2}.
Note that users can continue to edit the code while in this conflicted state.
It just must be resolved before the the code can be run.\footnote{
It may be possible to develop evaluation models that allow these sorts of conflicts,
but that is beyond the scope of this paper.}.

@@

@@

Before further exploring how to merge changes from multiple users,
we want to point out a common idiom that we call \emph{wrapping}.
Consider the first graph in Figure~\ref{fig:Wrapping}, which
represents the code \texttt{$\lambda$ x . x}, and suppose
the user's cursor is in the body field of the lambda (i.e., around the variable
reference to \texttt{x} in the body of the lambda).

@@

\subsubsection{Conflicting wrap operations}
Multi-parent

@@

>>>>

TODO: explain that multiple delete or add are idempotent

TODO: explain that delete overrides add

@@

\subsubsection{Multi-child conflicts}

@@

We merge these by including \emph{both} edges as edges going out of the \texttt{body} index
of node~3.
This results in the bottom graph of Figure~\ref{fig:Direct Conflicts}.
The conflict between Alice's and Bob's changes is
represented by the fact that there are multiple edges going out of one index (i.e. the \texttt{body}
index of node~3).
In the graph representation, we flag this conflict by highlighting its edges
in red.
In the textual representation, we flag this conflict with the notation \texttt{\{ 2 | f x \}}.
This is a conflict that much eventually be resolved by the user by deleting
one of the edges and editing the other to be the merged value.
For example, one could delete edge~10 and then edit the \texttt{x}
to be \texttt{x + 2}.
Note that users can continue to edit the code while in this conflicted state.
It just must be resolved before the the code can be run.\footnote{
It may be possible to develop evaluation models that allow these sorts of conflicts,
but that is beyond the scope of this paper.}

@@

\subsubsection{Multi-parent conflicts}

In addition to conflicts due multiple edges coming \emph{out of} an index of a particular vertex,
conflicts can manifest as multiple edges going \emph{into} a particular vertex.
We call these \emph{multi-parent conflicts}.

\begin{figure}
\centering

TODO TOP: +(\hole, +(\hole, x))

TODO LEFT: +(x, +(\hole, \hole))

TODO RIGHT: +(\hole, +(x, \hole))

TODO BOTTOM: Two parents pointing to x

\caption{Multi-parent conflict}
\label{fig:Multi-parent conflict}
\end{figure}

An example of this is shown in Figure~\ref{fig:Multi-parent conflict},
which starts with the top graph, which represents the expression \texttt{\hole + (\hole + x)}.
Suppose Alice moves the variable \texttt{x} to the left-most hole.
This results in the left graph, which represents the expression \texttt{x + (\hole + \hole)}.
At the same time, suppose Bob moves the variable \texttt{x} to the right-most hole.
This results in the right graph, which represents the expression \texttt{\hole + (x + \hole)}.
In both cases, these edits are achieved with one edge delete and one edge add.
Alice deletes edge TODO and adds edge TODO, while Bob deletes edge TODO and adds edge TODO.
As explained in Subsection~TODO:REF, deletes are idempotent so both Alice and Bob deleting
edge TODO is not a problem.
However, both edge TODO (added by Alice) and edge TODO (added by Bob) point to the same vertex.
This generates the bottom graph, in which vertex TODO as two parents pointing to it.
We call this situation a multi-parent conflict.

@@

Before \marginpar{DEL?} further exploring how to merge changes from multiple users,
we want to point out a common idiom that we call \emph{wrapping}.
Consider the first graph in Figure~\ref{fig:Wrapping}, which
represents the code \texttt{$\lambda$ x . x}, and suppose
the user's cursor is in the body field of the lambda (i.e., around the variable
reference to \texttt{x} in the body of the lambda).

@@

\subsubsection{Conflicting wrap operations}

@@

If two different 
As seen in REF:SEC:TODO, conflicting wraps gener

Multi-parent
